Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia

### 2015-05-26 nlpcc/paper.tex
改了一半了，让我喘喘

\subsubsection{Infobox-properties}
Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. Each attribute in the infobox is related to its own corresponding value. The value maybe a text or a reference to another entity. The type of a property, datatype or object, depends on the type of the value. Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as objecttype. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. Meanwhile, 导演(directed by) can be an object property because its value points to a person who directed the movie.

We are challenged when extracting properties from infoboxes:
\begin{itemize}
    \item The attribute label displayed in the webpage infobox is inconsistent with it in the published dump file of Wikipedia. Fig.\ref{fig:infobox-template} gives a mapping result of display label and dump label in \emph{Interstellar}' infobox. The left is infobox while the other is a snap from dump file in Wikipedia. This movie's infobox follows template \emph{Infobox film}, where dump labels come from. Obviously the two labels are similar but not the same. As a result we have to explore the display labels in Wikipedia rather than dump labels extracted from data file. As to Chinese sources, the property labels from Hudong Baike and Baidu Baike are equal literally to texts displayed on the webpage, so we don't need extra process as we have in Wikipedia.
    \begin{figure}[ht]
        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
        \label{fig:infobox-template}
        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
    \end{figure}%
    \item There are special characters in labels. For example, Wikipedia usually use hyphen "-" or dot "•" to mark sublabels. For example, population property have sub-properties "-Density" and "-Urban". In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
\end{itemize}

@@

\subsection{Instance Extraction}
\label{sec:ie}
In encyclopedia, an article describes an unique entity in the world. Therefore we can extract an article content as an instance. But we can't transform all the articles as instances because there are many illustrative or structure-related articles in Wikipedia, including category List pages and template documentations.

Each instance contains relations with concepts and properties. Take the movie 星际穿越(Interstellar) in Fig.\ref{fig:interstellar} as an example, concepts are assigned according to the category tags below the article page. 美国科幻片(American science fiction films) is a concept of Interstellar. In the meantime, we obtain the label property from the article title, which is 星际穿越(Interstellar) and the abstract property from the first paragraph. The infobox-properties are also acquired via extracting from the infobox in the article. Besides, according to links in the content, we gain the reference between the current instance and others, such as 华纳兄弟(Warner Bros.).

After the preprocessing above, we harvest two types of information. One is the characteristics of instance, including instance-label, instance-abstract. The other includes relationships, containing concept-instance, instance-property-value and instance-instance.

\section{Cross-lingual Knowledge Base Building}
\label{sec:clkbb}
To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set. Secondly, we link this four encyclopedia, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing. Thirdly, we prune the taxonomy generated from concept relationships to retain a more accurate one. At last, we make instances and properties attached to the taxonomy to create a complete knowledge base.

@@

However, due to following templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps: (1) Given a matched template, which has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, find the matched label mapping to the same dump label. (3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity. The whole process can be summarized as Algorithm \ref{alg:ple}. Some of the symbols have already denoted in \ref{sed:definition}
\subsection{Cross-lingual Linking}
In order to make all these encyclopedias linked to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers. For example, we merge instances by the following method:

\begin{enumerate}[1)]
    \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in Baidu Baike with the same title.
    \item Other instances existing in only one encyclopedia are considered as independent instances. Up to now, we have combined all Chinese articles describing the same entity as one instance. Each instance may correspond to 1 to 3 sources.
    \item To a $L_{z}(a)$, which is same as $Ti(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an new ID.
\end{enumerate}

After the above steps, we acquire a list of instances and their unique IDs. Some of them contain cross-lingual information while some contain just monolingual information.

@@

\subsection{Taxonomy Prune}
\label{sec:tp}
As a result of combining multi-source information without verifying, the taxonomy of concept system is mussy. For example, \textcolor{red}{example}. Therefore, we introduce the method from\cite{wang2014cross} to filter the correct subClassOf and instanceOf relations between two entities. Table. \ref{tab:} shows some examples of correct relations. In particular, some language-dependent literal and language-independent structural features are defined to vectorize each concept or instance. The literal features include the head words’ singular/plural forms of labels of English entities, the preﬁx/sufﬁx relation of labels of Chinese entities. The structural features include article divergence for subClassOf, property divergence for subClassOf, category divergence for subClassOf, article divergence for instanceOf, property divergence for instanceOf, category divergence for instanceOf. By employing these features, a binary-classification model is trained based on Logistic Regression. The whole process is iterative by add assured result into training set and retraining the model to get higher precision. Confirming a right subClassOf or instanceOf not only depends on the prediction result of classification, but also cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are correct. Fig. \ref{fig:} shows an example of the process.

The ideal result of pruning is a tree, whose edges denote relations, nodes denote concepts and leaves denote instances. However, since get rid of incorrect entity relations without consideration of integrity, getting a forest result is inevitable. We may omit some links but get more accurate relations instead.

\subsection{Knowledge Base Building}
To build a knowledge base, we first define specific URI to identify each element in the prepared dataset. URIs of concept, instance, and property are created by concatenating a namespace prefix to an ID. Table \ref{tab:uris} lists the URI defined in the knowledge base.
\begin{table}[h]
\small
\centering
\caption{URIs for concept, instance, property in our knowledge base}
\label{tab:uris}
    \begin{tabular}{|c|c|}
        \hline
        Type     & URI                          \\ \hline
        Concept  & http://xlore.org/concept/id  \\ \hline
        Instance & http://xlore.org/instance/id \\ \hline
        Property & http://xlore.org/property/id \\ \hline
    \end{tabular}
\end{table}

\section{Result}
\label{sec:result}
\subsection{DataSet}
四个百科的数据统计，包括我们有的百科数据的发布时间，格式（xml。html），article数量，抽取的instance数量，concept数量，property数量, wiki中跨语言链接数量
其实最好有一些我们在抽取过程中删剪的不符合要求的concept或者property数量，不过要看有没有时间再跑一下了
\subsection{Extracted Knowledge Base}
We collect the resources from 4 wiki sites, Enwiki, Zhwiki, Hudong, and Baidu. Each of the wikis has three types of information, which can be utilized for constructing our ontology, namely, specific articles, classification system, and attribute of articles. We extract each raw data, then form the extracted information into well-structured data. Table\ref{tab:extract-result} the result we get after elementary extraction in 4 different wiki sources.

@@

\section{Related Work}
\label{sec:work}
In this section, we introduce some related knowledge bases and cross-lingual knowledge linking methods are referred to.
\subsection{Chinese Knowledge Bases}
Currently, several large-scale Chinese knowledge bases have been generated. Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first Chinese large-scale Linking Open Data published. It acquires structural information from three original sources, Chinese Wikipedia, Baidu Baike and Hudong Baike and gains more than 5 million distinct entities. Zhishi.me helps generate knowledge base focused on relations in Junfeng Pan’s work\cite{pan2012building}.
Similar with Zhishi.me, CKB\cite{wang2012building} is created from Hudong Baike. It first learns an ontology based on category system and properties, and then collects 19542 concepts, 2381 properties, 802593 instances. Besides using existing encyclopedias, CASIA-KB employs other types of sources(e.g. microblog posts, news pages, images) to enrich the structured knowledge.
\subsection{Cross-lingual Knowledge Bases}
DBpedia \cite{auer2007dbpedia,mendes2012dbpedia} is one of the most used cross-lingual knowledge base in the world. It's extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content. This knowledge base is widely applied in many domains, including media recommendation \cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
Universal WordNet(UWN)\cite{de2012uwn} is a large multilingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia. It is constructed using sophisticated knowledge extraction, link prediction, information integration, and taxonomy induction methods. The API is available to over 200 languages and more than 16 million words and names. UWN provides semantic relationship of list of word meanings for Aya's work on conceptual search \cite{al2015conceptual}

@@

\section{Conclusion}
\label{sec:con}
This paper presents a procedure of building a Chinese-English cross-lingual knowledge base from four encyclopedia sources. At first, data preprocessing work is done to extract structured information and unify data format. Then a cross-lingual lan-link set is generated to help combine the bilingual sources. Besides, an extension method is applied to enrich the links. To refine our dataset, we also do pruning work on taxonomy. Finally, we acquire a knowledge base containing XXX concepts, XXX instances and XXX properties. Currently, a SPARQL query interface is provided to access the knowledge base.

>>>>

\subsubsection{Infobox-properties}
Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. All attributes relate with a typical value in the infobox. The value maybe a text or a reference to another entity. The type of a property, datatype or object, depends on the value. Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as object. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. Meanwhile, 导演(directed by) can be an object property because its value points to a person who directed the movie.

We occur some challenges when extracting properties from infoboxes:
\begin{itemize}
    \item The attribute label displayed in webpage infobox is inconsistent with it in dump file of Wikipedia. Fig.\ref{fig:infobox-template} gives a mapping result of display label and dump label in \emph{Interstellar}' infobox. The left is infobox while the other is a snap from dump file in Wikipedia. This movie's infobox follows template \emph{Infobox film}, where dump labels come from. Obviously the two labels are similar but not the same. As the property labels from Hudong Baike and Baidu Baike are equal to text displayed on the webpage, we have to explore the display labels in Wikipedia rather than dump labels extracted from data file.
    \begin{figure}[ht]
        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
        \label{fig:infobox-template}
        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
    \end{figure}%
    \item There are special characters in labels. For example, Wikipedia usually use hyphen "-" or dot "•" to mark sublabels. Population property have sub-properties of "Density" and "Urban". In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
\end{itemize}

@@

\subsection{Instance Extraction}
\label{sec:ie}
In encyclopedia, an article describes an unique entity in the world. Therefore we can extract article content as an instance. But we can't transform all the articles as instances because there are many illustrative or structure-related articles in Wikipedia, including category List pages and template documentations.

Each instance contains relations with concepts and properties. Take the movie 星际穿越(Interstellar) in Fig.\ref{fig:interstellar} as an example, concepts are assigned according to the category tags below the article page. 美国科幻片(American science fiction films) is a concept to Interstellar. In the meantime, we obtain label property from article title, which is 星际穿越(Interstellar) and abstract property from the first paragraph. Infobox-properties are also acquired via extracting from infobox in the article. Besides, according to links placing in content, we gain the reference between the current instance to others, such as 华纳兄弟(Warner Bros.).

After the preprocessing above, we harvest two types of information. One is the characteristics of instance, including instance-label, instance-abstract. The other is relationships, containing concept-instance, instance-property-value and instance-instance.

\section{Cross-lingual Knowledge Base Building}
\label{sec:clkbb}
To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set. Secondly, we link the four encyclopedia, which is to say, combining concept, instance and property of the four sources into one if it represents the same thing. Thirdly, we prune the taxonomy which generates from concept relationships to retain a more accurate one. At last, we hung instances and properties on to taxonomy to create a complete knowledge base.

@@

However, due to following templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we go through the following steps: (1) Given a matched template, that is a template has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare the templates they use, find the matched label mapping to the same dump label. (3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity. The whole process can be summarized as Algorithm \ref{alg:ple}. Some of the symbols have already denoted in \ref{sed:definition}
\subsection{Cross-lingual Linking}
In order to make the ontology of one encyclopedia link to others, we unify the same concept, instance and property from four source to unique one and make identifier. For example, we merge instances by the following method:

\begin{enumerate}[1)]
    \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in BaiduBaike with the same title.
    \item The other instances existing in only one encyclopedia are considered as an independent instance. Up to now, we have combined all Chinese articles describing the same entity as one instance. Each instance may correspond to 1 to 3 sources.
    \item To a $L_{z}(a)$, which is same as $Ti(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an independent ID.
\end{enumerate}

After the above steps, we acquire a list of instances and their unique IDs. Some of them contain cross-lingual information while some contain monolingual.

@@

\subsection{Taxonomy Prune}
\label{sec:tp}
As a result of combining multi source information without verifying, the taxonomy of concept system is mussy. For example, \textcolor{red}{example}. Therefore, we introduce the method from\cite{wang2014cross} to filter the correct subClassOf and instanceOf relations between two entities. Table. \ref{tab:} shows some examples of correct relations. In particular, some language-dependent literal and language-independent structural features are defined to vector each concept or instance. The literal features include the head words’ singular/plural forms of labels of English entities, the preﬁx/sufﬁx relation of labels of Chinese entities. The structural features include article divergence for subClassOf, property divergence for subClassOf, category divergence for subClassOf, article divergence for instanceOf, property divergence for instanceOf, category divergence for instanceOf. By employing these features, a binary-classification model is trained based on Logistic Regression. The whole process is iterative by add assured result into training set and retraining the model to get higher precision. Confirming a right subClassOf or instanceOf not only depends on the prediction result of classification, but also related with cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are right. Fig. \ref{fig:} shows an example of the process.

The ideal result of pruning is a tree, whose lines denote relations, nodes denote concepts and leaves denote instances. However, with wrong relations cut without caring about integrity, getting a forest is inevitable. We may lose some links but get more accurate relations instead.

\subsection{Knowledge Base Building}
To build a knowledge base, we first define specific URI to identify each element in the prepared dataset. URIs of concept, instance, and property are created by concatenating a namespace prefix and ID. Table \ref{tab:uris} lists the URI defined in the knowledge base.
\begin{table}[h]
\small
\centering
\caption{URIs for concept, instance, property in our knowledge base}
\label{tab:uris}
    \begin{tabular}{|c|c|}
        \hline
        Type     & URI                          \\ \hline
        Concept  & http://xlore.org/concept/id  \\ \hline
        Instance & http://xlore.org/instance/id \\ \hline
        Property & http://xlore.org/property/id \\ \hline
    \end{tabular}
\end{table}

\section{Result}
\label{sec:result}
\subsection{DataSet}
四个百科的数据统计，包括我们有的百科数据的发布时间，格式（xml。html），article数量，抽取的instance数量，concept数量，property数量, wiki中跨语言链接数量
其实最好有一些我们在抽取过程中删剪的不符合要求的concept或者property数量，不过要看有没有时间再跑一下了
\subsection{Extracted Knowledge Base}
We collect the resources from 4 wiki sites, Enwiki, Zhwiki, Hudong, and Baidu. Each of the wikis has three types of information, which can be utilized for building our ontology, namely, specific articles, classification system, and attribute of articles. We extract each raw data, then form the extracted information into well-structured data. Table\ref{tab:extract-result} the result we get after elementary extraction in 4 different wiki sources.

@@

\section{Related Work}
\label{sec:work}
In this section, we introduce some related knowledge bases and cross-lingual knowledge linking methods are referred to.
\subsection{Chinese Knowledge Bases}
Currently, several large-scale Chinese knowledge bases have been generated. Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first large-scale Linking Open Data published. It acquires structural information from three original sources, Chinese Wikipedia, BaiduBaike and Hudong and gets more than 5 million distinct entities. Zhishi.me helps generate knowledge base focused on relations in Junfeng Pan’s work\cite{pan2012building}.
Similar with Zhishi.me, CKB\cite{wang2012building} is created from Hudong Baike. It first learns an ontology based on category system and properties, and then collects 19542 concepts, 2381 properties, 802593 instances. Besides using existing encyclopedias, CASIA-KB employs other types of sources(e.g. microblog posts, news pages, images) to enrich the structured knowledge.
\subsection{Cross-lingual Knowledge Bases}
DBpedia \cite{auer2007dbpedia,mendes2012dbpedia} is one of the most used cross-lingual knowledge base in the world. It's extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content. This knowledge base is widely applied in many domain, including media recommendation \cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}.
Universal WordNet(UWN)\cite{de2012uwn} is a large multilingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia. It is constructed using sophisticated knowledge extraction, link prediction, information integration, and taxonomy induction methods. The API is available to over 200 languages and more than 16 million words and names. UWN provides semantic relationship of list of word meanings for Aya's work on conceptual search \cite{al2015conceptual}

@@

\section{Conclusion}
\label{sec:con}
